### 2019-01-21 macro3_1.tex
Macro

	In the same time the current value is decreasing, which can be inferred from $\frac{V'(k(t))}{V'(k(t+1))} = \beta < 1$.

@@

\item 

>>>>

	In the same time the current value is increasing, which can be inferred from $\frac{V'(k(t))}{V'(k(t+1))} = \beta < 1$.

@@

\item Now FOCs are:
\begin{cases}\frac{\partial}{\partial c(t)}: u'(c(t)) - \lambda(t) = 0\\
\frac{\partial}{\partial k(t+1)}: -\beta^t \lambda(t) + \beta^{t+1}(1 - \delta)\lambda(t+1) = 0\\
\frac{\lambda(t+1)}{\lambda(t)} = \frac{1}{\beta(1 - \delta)} > \frac{1}{\beta}
that means that in this case even present value will increase over time:
V'(k(t)) = \frac{1}{(1 - \delta)^t}V'(k(0))
and the rate of increasing of current value $\frac{1}{\beta(1-\delta)}$ goes up compare to the case $\delta = 0$.
